### 2020-04-20 final_report/methodology.tex
write experiments section

TODO: single slice hyperparameter optimisation

TODO: multislice (mixed) hyperparameter optimisation

TODO: retraining for scaling benchmark

TODO: retraining on large set

\newpage

>>>>

The presented surrogate candidates are evaluated in four experimental cases:

\begin{enumerate}

	\item Hyperparameter tuning in simplified domain,

	\item Hyperparameter tuning in full domain,

	\item Scaling benchmark,

	\item Competitive surrogate training.
\end{enumerate}

The aim of the initial experiments is to use a relatively small subset of
collected TBR samples to determine hyperparameters of considered surrogates.
Since this process requires learning the behaviour of an unknown, possibly
expensive mapping---here a function that assigns cross-validated metrics to a
point in the hyperparameter domain---it in many aspects mirrors
the primary task of this work with the notable extension of added utility
to optimise. In order to avoid undesirable exponential slowdown in exhaustive
searches of a possibly high-dimensional parameter space, Bayesian
optimisation is employed as standard hyperparameter tuning algorithm that is considered
efficient for this purpose. We set its objective to maximise $R^2$.

In the first experiment, efforts are made to maximise the possibility of success
in surrogates that are prone to suboptimal performance in discontinuous spaces.
This follows the notion that, if desired, accuracy of such models may be
replicated at large scale by decomposing the TBR domain into continuous subsets,
and learning ensemble surrogate comprised of models that are trained on each
subset independently, incurring exponential complexity penalty in the process.
To this end, training samples are filtered to only contain a single assignment
of discrete features that are subsequently completely withheld from evaluated
surrogates. This is repeated four times to investigate variance in behaviour
under different feature assignments.

The second experiment conventionally measures surrogate performance on the full
TBR regression task. In extension of the previous case, surrogates work with
unfiltered samples comprised of discrete as well as continuous features.

The goal of the last two experiments is to exploit the information gathered by
hyperparameter tuning for study of scaling properties. In
the third experiment, the best-performing hyperparameter choices of each class
are used to learn surrogates using progressively larger training sets. Following
that, the fourth experiment attempts to produce competitive surrogates by
retraining several selected well-scaling models on the largest available data set.
